Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
paper: add load balancing problem to section 3
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

A storage system implements abstractions designed to persistently store
data and must exhibit a high level of correctness to prevent data loss.
Storage systems have evolved around storage devices that often were
orders of magnitude slower than CPU and memory, and therefore could
dominate overall performance if not used carefully. Over the last few
decades members of the storage systems community have developed
ingenious strategies to meet correctness requirements while somewhat
hiding the latency of traditional storage media~\cite{brewer_disks_2016}. To avoid lock-in by a
particular vendor, users of storage systems have preferred systems with
highly standardized APIs and lowest common denominator abstract data
types such as blocks of bytes and byte stream files~\cite{armbrust_view_2010}.

A number of recent developments are disrupting traditional storage
systems: (1) the falling prices of flash storage and the availability of
new types of non-volatile memory that are orders of magnitude faster
than traditional spinning media are moving overall performance
bottlenecks away from storage devices to CPUs and networking, and
pressure storage systems to shorten their code paths and incorporate new
optimizations~\cite{gray_tape_2007,gray_flash_2008}; (2) demand for managing structured data and flexible
consistency semantics at scale pressure big data processing systems to
use storage abstractions that can meet these demands~\cite{apache_contributors_parquet_2014}; and (3)
production-quality scalable storage systems available as open source
software have established and are continuing to establish new, \emph{de
facto} API standards at a faster pace than traditional standards bodies~\cite{snia_implementing_2014,linux_foundation_kinetic_2015}.

@@

To illustrate the benefits and challenges of this approach we examine
the programmability of Ceph~\cite{weil_ceph_2006}, the increasingly
popular, production-level open-source distributed storage system.
Something of a storage swiss army knife, Ceph supports file, block, and
object interfaces simultaneously in a single cluster~\cite{ceph_contributors_ceph_2010}. Ceph's Reliable Autonomous 
Distributed Object Storage (RADOS) system is a cluster of storage
devices (OSDs) that provide Ceph with data durability and integrity
using replication, erasure-coding, and scrubbing~\cite{weil_rados_2007}. 
% By introducing
% programmability concepts into Ceph, we can build new services by
% carefully exposing internal storage services to applications.

@@

@@

Many distributed file systems decouple metadata and data I/O so that
these services can scale independently~\cite{alam:pdsw2011-metadata-scaling,ghemawat:sosp2003-gfs,hildebrand:msst2005-pnfs,weil_ceph_2006,welch:fast2008-panasas,shvachko:login2012-hdfs-scalability}. Despite
this optimization, scaling the metadata services is still difficult
because metadata accesses impose small and frequent requests on the
underlying storage syste~\cite{roselli:atec2000-FS-workloads}. Many
techniques for designing the metadata services have been proposed to
accommodate this workload: Lustre~\cite{konstantinos:pdsw2014-lustre-metadata}, GFS~\cite{ghemawat:sosp2003-gfs}, and HDFS~\cite{shvachko:login2012-hdfs-scalability} keep all metadata on one
server; GIGA+~\cite{patil:fast2011-giga}, IndexFS~\cite{ren:sc2014-indexfs}, Lazy Hybrid~\cite{brandt:msst2003-lh}, GPFS~\cite{schmuck:fast2002-gpfs},
and pNFS~\cite{hildebrand:supercomputing2006-pNFS} hash the file
system namespace across a dedicated cluster and cache metadata; Panasas~\cite{welch:fast2008-panasas} and CephFS~\cite{weil:sc2004-dyn-metadata} partition the file system namespace
into \# d assign them to servers. These systems have novel mechanisms
for Mantle~\cite{sevilla:sc15-mantle} is a programmable metadata
balancer that separates the metadata balancing policies from their
mechanisms. Admistrators inject code to change how the metadata cluster
distributes metadata. In the paper, we showed how to implement a single
node metadata service, a distributed metadata services with hashing, and
a distributed metadata service with dynamic subtree partitioning.

@@

>>>>

A storage system implements abstractions designed to persistently store
data and must exhibit a high level of correctness to prevent data loss.
Storage systems have evolved around storage devices that often were
orders of magnitude slower than CPU and memory and therefore can
dominate overall performance if not used carefully. Over the last few
decades members of the storage systems community have developed
ingenious strategies to meet correctness requirements while somewhat
hiding the latency of traditional storage media. To avoid lock-in by a
particular vendor, users of storage systems have preferred systems with
highly standardized APIs and lowest common denominator abstract data
types such as blocks of bytes and byte stream files.

A number of recent developments are disrupting traditional storage
systems: (1) the falling prices of flash storage and the availability of
new types of non-volatile memory that are orders of magnitude faster
than traditional spinning media are moving overall performance
bottlenecks away from storage devices to CPUs and networking, and
pressure storage systems to shorten their code paths and incorporate new
optimizations; (2) demand for managing structured data and flexible
consistency semantics at scale pressure big data processing systems to
use storage abstractions that can meet these demands; and (3)
production-quality scalable storage systems available as open source
software have established and are continuing to establish new, \emph{de
facto} API standards at a faster pace than traditional standards bodies.

@@

To illustrate the benefits and challenges of this approach we examine
the programmability of Ceph~\cite{weil_ceph_2006}, the increasingly
popular, production-level open-source distributed storage system.
Something of a storage swiss army knife, Ceph supports file, block, and
object interfaces simultaneously in a single cluster. Ceph's Reliable Autonomous Distributed Object Storage (RADOS) system is a cluster of storage
devices (OSDs) that provide Ceph with data durability and integrity
using replication, erasure-coding, and scrubbing~\cite{weil_rados_2007}. 
% By introducing
% programmability concepts into Ceph, we can build new services by
% carefully exposing internal storage services to applications.

@@

\subsection{Load Balancing}

% Straw man example
Migrating resources is an important part of load balancing but understanding the effects of different configurations and parameters is difficult. Systems already virtualize and migrate memory; soon systems will be able to migrate other resources, like CPU, disk, and memory. Figuring out how, when, and where to move these resources depends on complex metrics like utilization, configuration, and workload.

These problems are general, distributed systems load balancing problems and share many of the same properties as the POSIX metadata wall~\cite{alam:pdsw2011-metadata-scaling,ghemawat:sosp2003-gfs,hildebrand:msst2005-pnfs,weil_ceph_2006,welch:fast2008-panasas,shvachko:login2012-hdfs-scalability}. Many distributed file systems decouple metadata and data I/O so that
these services can scale independently. Despite
this optimization, scaling the metadata services is still difficult
because metadata accesses impose small and frequent requests on the
underlying storage system~\cite{roselli:atec2000-FS-workloads}. Many
techniques for designing the metadata services have been proposed to
accommodate this workload: Lustre~\cite{konstantinos:pdsw2014-lustre-metadata}, GFS~\cite{ghemawat:sosp2003-gfs}, and HDFS~\cite{shvachko:login2012-hdfs-scalability} keep all metadata on one
server; GIGA+~\cite{patil:fast2011-giga}, IndexFS~\cite{ren:sc2014-indexfs}, Lazy Hybrid~\cite{brandt:msst2003-lh}, GPFS~\cite{schmuck:fast2002-gpfs},
and pNFS~\cite{hildebrand:supercomputing2006-pNFS} hash the file
system namespace across a dedicated cluster and cache metadata; Panasas~\cite{welch:fast2008-panasas} and CephFS~\cite{weil:sc2004-dyn-metadata} use subtree partitioning to carve up the namespace and distribute it across a cluster.

CephFS moves units of the namespace called directory fragments and assigns them to servers using  its own metadata load balancer. It then uses a hard-coded policy to balance these fragments using a secularized load metric based on CPU, workload, and file system operation metrics~\cite{sevilla:sc15-mantle}.

@@

Mantle~\cite{sevilla:sc15-mantle} is a programmable metadata
balancer for Ceph that separates the metadata balancing policies from their
mechanisms. Administrators inject code to change how the metadata cluster
distributes metadata. In the paper, we showed how to implement a single
node metadata service, a distributed metadata services with hashing, and
a distributed metadata service with dynamic subtree ipartitioning.

@@

We implemented it using the components from section 3. I will tell you about them here.
